Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-02-07 public/paper/pyg4ometry.tex
Correct names of classes in table

\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|} \hline
FLUKA body							& pyg4ometry class 		\\ \hline
RPP 	(Rectangular parallelepiped)			& Box				\\
BOX	(General rectangular parallelepiped)		& Box				\\
SPH 	(Sphere)							& Orb				\\
RCC (Right circular cylinder)				& Cone				\\
REC (Right elliptical cylinder)				& EllipticalTube			\\
TRC (Truncated Right Angle Cone)			& Cone				\\
ELL (Ellipsoid of Revolution) 				& Ellipsoid				\\
WED/RAW (Right Angle Wedge)			& ExtrudedSolid		\\
ARB	(Arbitrary Convex Polyhedron)			& TessellatedSolid		\\
XYP 	($X$-$Y$ Infinite half-space)			& Box				\\
XZP 	($X$-$Z$ Infinite half-space)			& Box				\\
YZP 	($Y$-$Z$ Infinite half-space)			& Box				\\
PLA (Generic infinite half-space)			& Box				\\
XCC ($X$-axis Infinite Circular Cylinder)		& Tubs				\\
YCC ($Y$-axis Infinite Circular Cylinder)		& Tubs				\\
ZCC 	($Z$-axis Infinite Circular Cylinder)		& Tubs				\\
XEC 	($X$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
YEC 	($Y$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
ZEC ($Z$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
QUA (Quadric surface) 					& TessellatedSolid		\\ \hline
\end{tabular}
\caption{FLUKA geometry directives pyg4ometry classes.} \label{tab:Fluka2Geant4}
\end{table}

>>>>

\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|} \hline
FLUKA body						& pyg4ometry class \\ \hline
RPP (Rectangular parallelepiped)			& Box \\
BOX (General rectangular parallelepiped)		& Box \\
SPH (Sphere)    					& Orb \\
RCC (Right circular cylinder)				& Tubs \\
REC (Right elliptical cylinder)				& EllipticalTube \\
TRC (Truncated Right Angle Cone)			& Cons \\
ELL (Ellipsoid of Revolution) 				& Ellipsoid \\
WED/RAW (Right Angle Wedge)		         	& ExtrudedSolid \\
ARB	(Arbitrary Convex Polyhedron)			& TessellatedSolid \\
XYP 	($X$-$Y$ Infinite half-space)			& Box \\
XZP 	($X$-$Z$ Infinite half-space)			& Box \\
YZP 	($Y$-$Z$ Infinite half-space)			& Box \\
PLA (Generic infinite half-space)			& Box \\
XCC ($X$-axis Infinite Circular Cylinder)		& Tubs \\
YCC ($Y$-axis Infinite Circular Cylinder)		& Tubs \\
ZCC 	($Z$-axis Infinite Circular Cylinder)		& Tubs \\
XEC 	($X$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
YEC 	($Y$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
ZEC ($Z$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
QUA (Quadric surface) 					& TessellatedSolid \\ \hline
\end{tabular}
\caption{FLUKA geometry directives pyg4ometry classes.} \label{tab:Fluka2Geant4}
\end{table}
